Automatic Matching of Bullet Lands

### 2016-05-04 revision/response.Rmd

1. The paper should better explain the role of the new methods for forensic science. The authors should consider referencing some of the previous work the reviewers mention.

***AC: TODO***

2. Methodologically, the crux of the data analysis seems to be a generic application of decision trees. It would be good to clarify that aspect, and to more formally explain how the ensemble of the steps took by the authors to complete this work can be applied to other forensic science questions.

***We have detailed a multi-stage analysis process that begins with a source image, processes the image, extracts features, and ultimately uses a random forest to compute predicted match probabilities. While the forest is a component of the process, we've taken care to emphasize that the preceeding steps outline a more general framework for analysis of striae in images that could theoretically apply to other forensic science questions as well.

***EH: TODO: Add to paper***

@@

# Reviewer A

3. Random forests, as used and described on pages 18-21 of the paper comes out looking like a winner, but other than that success---worth reporting *somewhere*---, there is no new information on that method. No new insights. And certainly no comparisons with the tens of other things that could have been tried.

***HH: Could you look at this response i wrote?***

***We were not intending to provide new insights on random forests. The insights were in the feature extraction and image processing leading up to the random forest fit. As the forest ultimately predicted every land-to-land comparison properly, we felt that a comparison to other learning methods wass outside the scope of this paper. Had a wider variety of data been available, there would likely be more variability in the predictions and a comparison to other learning methods would be prudent. For this particular paper, however, the groove detection, profile extraction, and feature definitions were the intended focus.***

@@

***leon:2006 first sentence: "Fired bullets bear striation marks that can be thought of as a ‘‘fingerprint’’ left by the firearm." based on multiple 2d images. They extract a 1d 'signature'***

5. page 7- figure 4- What exactly are you bootstrapping? It is unclear in the paper whether you are bootstrapping residual or bullets or something else entirely. Please clarify.

***HH: will do***

6. There should have been a comparison of different classification methods to show that the random forest is reasonable.

***HH: I am not quite sure what a 'reasonable' classification method is supposed to mean. Shouldn't a classification method be judged by its success in predicting the outcome? Apart from that, random forests are based on decision trees, which are an extremely flexible tool for classification, that can deal with quantitative and categorical types of variables and, in the implementation we used, also deal with some missing values (which was not needed in the data here).***

7. On the random forest classifier- are the prior probabilities being estimated from the cross comparisons described on page 15? What exactly are the prior probabilities used in the random forest?

### 2016-05-06 revision/response.Rmd

1. The paper should better explain the role of the new methods for forensic science. The authors should consider referencing some of the previous work the reviewers mention.

***AC: TODO***

2. Methodologically, the crux of the data analysis seems to be a generic application of decision trees. It would be good to clarify that aspect, and to more formally explain how the ensemble of the steps took by the authors to complete this work can be applied to other forensic science questions.

***We have detailed a multi-stage analysis process that begins with a source image, processes the image, extracts features, and ultimately uses a random forest to compute predicted match probabilities. While the forest is a component of the process, we've taken care to emphasize that the preceeding steps outline a more general framework for analysis of striae in images that could theoretically apply to other forensic science questions as well.***

### 2016-05-07 imaging-paper.Rnw
Update response, add in new section to conclusion
added boxplots - densities do not work, because they are too skew

@@

By suggesting an automated algorithm that first removes class characteristics, such as the grooves and the curvature of the bullet to reveal the region of the  land, then identifies peaks and valleys on this land, we reduce subjectivity and with it possible sources of bias. In particular, `the concept of counting striations is subjective and based on experience'~\citep{miller:1998}.

>>>>

qplot(data=predm, value, geom="boxplot", fill=match, x=match, alpha=I(0.5)) + 
  theme_bw() + facet_grid(variable~.) +
  scale_fill_brewer(palette="Paired", labels=c("KNM", "KM")) +
   ylab("") + 
   xlab("Predicted probability of a match") +
  coord_flip() + 
  theme(legend.position="none")

@@

By suggesting an automated algorithm that first removes class characteristics, such as the grooves and the curvature of the bullet to reveal the region of the  land, then identifies peaks and valleys on this land, we reduce subjectivity and with it possible sources of bias. In particular, `the concept of counting striations is subjective and based on experience'~\citep{miller:1998}. \eh{The steps outlined in this paper could also help explore other important forensic science problems. In particular, more general toolmark examination can benefit from this detection and removal of the overall structure and the extraction of features from deviations of this structure.}
